Can Cultural Transmission Explain The Evolution of Cooperative Behavior?

### 2020-04-23 ms/main.tex
added explanation for alpha=1

%\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx} % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
% TeX will automatically convert eps --> pdf in pdflatex

@@

\textbf{Result 1: Vertical and horizontal transmission of cooperation.}
If 
\begin{equation} \label{eq:unequal_transmission}
c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + b\tilde{p}(1-\alpha)]
\end{equation}
then $\tilde{p}' > \tilde{p}$, and the frequency of phenotype $A$ among parents increases. 
\\

\textbf{Corollary 1.1: equal horizontal transmission.}
If $T=T_A=T_B$, then
\begin{equation}
\label{eq:equal_transmission}
\frac{1-T}{\alpha T} < \frac{b}{c},
\end{equation}
which can be seen as a cultural version of \emph{Hamilton's rule} (eq.~\ref{eq:hamilton_rule}).

@@

In this case, horizontal transmission can only occur as a result of cooperative interactions.
\\Eq.~\ref{eq:unequal_transmission} becomes:
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_only_after_interaction}
c\cdot(1-T_B)  < \,& T_A\cdot(1+b) - T_B
\end{split}
\end{equation}
Therefore, cooperative behavior will take over the population when eq.~\ref{eq:horizontal_transmission_only_after_interaction} is satisfied. 
This result is in accordance with the result presented by~\citet{lewin2017microbes}.

>>>>

\usepackage[parfill]{parskip} % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx} % Use pdf, png, jpg, or eps§ with pdflatex; use eps in DVI mode
% TeX will automatically convert eps --> pdf in pdflatex

@@

\textbf{Result 1: Vertical and horizontal transmission of cooperation.}
If 
\begin{equation} \label{eq:unequal_transmission}
c \cdot (1-T_B) < b \cdot  \alpha T_A  + (T_A - T_B) [1 + b\tilde{p}(1-\alpha)]
\end{equation}
then $\tilde{p}' > \tilde{p}$, and the frequency of phenotype $A$ among parents increases.

\textbf{Corollary 1.1: Equal horizontal transmission.}
If $T=T_A=T_B$, then
\begin{equation}
\label{eq:equal_transmission}
\frac{b}{c} > \frac{1-T}{\alpha T},
\end{equation}
which can be seen as a cultural version of \emph{Hamilton's rule} (eq.~\ref{eq:hamilton_rule}).

@@

In this case, horizontal transmission can only occur as a result of cooperative interactions.
Therefore, eq.~\ref{eq:unequal_transmission}, which determines the conditions for evolution of cooperation, becomes
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_only_after_interaction}
T_A b > \,& c (1-T_B) + (T_B - T_A).
\end{split}
\end{equation}
This is equivalent to a result by~\citet[eq.~1]{lewin2017microbes}.
Eq.~\ref{eq:horizontal_transmission_only_after_interaction} can be written as
\begin{equation} 
\begin{split} \label{eq:horizontal_transmission_only_after_interaction2}
T_A\cdot(1+b) > \,& 1 - (1-T_B)(1-c).
\end{split}
\end{equation}
This equation provides an interesting interpretation for the success of cooperation. 
Consider an interaction between two individuals: a cooperator and a defector.
$T_A\cdot(1+b)$ is the probability that the defector becomes cooperative and reproduces.
This is the effective benefit for cooperation from this interaction.
$(1-T_B)(1-c)$ is the probability that the cooperator remains cooperative and also reproduces. 
Therefore, $1 - (1-T_B)(1-c)$ is the probability that either the cooperator becomes a defector, \emph{or} that it fails to reproduce.
This is the effective cost for cooperation from this interaction.
So, eq.~\ref{eq:horizontal_transmission_only_after_interaction2} means that cooperation can evolve if effective benefit is larger than the effective cost.
